\section{Introduction}

Effectively parsing video content is a fundamental requirement for many
downstream applications such as video indexing, content retrieval,
summarization, and automated editing. Within this pipeline, shot boundary
detection (SBD) serves as a critical preliminary step: it partitions a video
into temporally coherent shots by identifying frames where camera
views, scene contents, or editing states transition
\cite{seridi2020survey,kar2024review}. Classical methods based on
hand-crafted cues such as color histograms and motion differences are
efficient but fragile under fast camera motion, flashes, and modern editing
styles \cite{abdulhussain2018review}.

Deep architectures such as TransNet and TransNetV2
\cite{soucek2019transnet,soucek2020transnetv2} learn spatiotemporal
representations directly from frame sequences and have advanced modern SBD
systems. Concurrently, the rise of short-video
platforms (e.g., TikTok, YouTube Shorts) has introduced a new, challenging
operating regime: brief videos, dense editing, and heavy special effects. To
address it, AutoShot \cite{zhu2023autoshot} leverages neural architecture
search (NAS) to select a 3-D convolutional backbone, demonstrating notable
performance on the newly introduced SHOT dataset. Further improving these
models, however, encounters a practical bottleneck: the NAS pipeline requires
substantial computation for supernet training and architecture evaluation.
Moreover, short-video SBD suffers from extreme
class imbalance --- boundary frames are exceptionally rare --- and complex
visual effects that act as hard negatives.

We study an alternative refinement path that separates the frozen
representation from the decision stage. Instead of re-running the NAS process
or updating the searched AutoShot backbone, AutoShotV2 trains a compact
classification head on cached 4864-dimensional features. This frozen-feature
setting isolates a decision-stage design space: binary cross-entropy, Focal
Loss \cite{lin2017focal}, and boundary-aware many-hot supervision can be
compared without changing the representation. Because SBD decisions are made
by thresholding scores, the decision stage also includes probability
calibration and temporal smoothing. Temperature scaling
\cite{guo2017calibration} rescales logits without changing their ranking,
and a one-dimensional Gaussian filter suppresses isolated peaks caused by
flashes, camera motion, or short-lived visual effects.

Under per-dataset threshold selection, AutoShotV2 achieves F1 scores of 0.8607 on SHOT, 0.9656 on BBC, and 0.7706 on ClipShots, outperforming the reproduced AutoShot baseline by 2.02, 1.02, and 0.57 percentage points, respectively. Under a single fixed deployment threshold, the framework achieves 0.8545, 0.9656, and 0.7529 F1. A controlled replication under a frozen, validation-only five-fold protocol separates training choices from post-processing choices: the training-loss alternatives change F1 only marginally, whereas calibrated post-processing adds \PaperBFourVsAOneShotPP{} percentage points on SHOT and \PaperBFourVsAOneClipPP{} percentage points on ClipShots in F1 over the BCE control. Paired bootstrap intervals support the positive deltas on SHOT and ClipShots, but not on BBC.

In summary, our main contributions are:
\begin{itemize}
\item We propose AutoShotV2, an efficient frozen-feature SBD refinement pipeline that improves reproduced AutoShot under per-dataset operating-point selection, reaching F1 scores of 0.8607 on SHOT, 0.9656 on BBC, and 0.7706 on ClipShots.
\item We separate domain-specific operating-point analysis from fixed-threshold deployment evaluation, showing that the same framework reaches 0.8545, 0.9656, and 0.7529 F1 under a single deployment threshold on SHOT, BBC, and ClipShots.
\item We evaluate compact head variants and a loss-design space, including Focal Loss and boundary-aware many-hot supervision, and show that most of the performance gain is attributable to calibrated post-processing, while alternative training losses do not add consistent gains.
\item We define a validation-only, source-stratified selection protocol that fixes temperature, smoothing, and threshold before test evaluation, and we quantify uncertainty with paired video bootstrap intervals and calibration diagnostics including adaptive and class-balanced ECE.
\item We report experiments on SHOT, BBC, and ClipShots with cache identity checks, split/run manifests, a three-seed robustness study, and checksum-based artifact packaging.
\end{itemize}

This paper employs two complementary evaluation tracks. The fixed-deployment checkpoint provides the deployment robustness analysis and is preserved through tracked, checksummed result files. A controlled replication with full logit caches anchors the logit-level confidence intervals, calibration diagnostics, ablations, and seed study (Section~\ref{sec:tracks}).
