\section{Related Work}

\textbf{Shot boundary detection.} Shot boundary detection has long been a
central task in video processing. Early systems detect frame-to-frame
discontinuities with hand-crafted cues such as color histograms,
edge-change ratios, motion compensation, and thresholding heuristics. These
methods are computationally simple, but they often confuse lighting changes,
camera motion, or object movement with actual boundaries
\cite{abdulhussain2018review}. Survey studies group the main challenges
around abrupt cuts, gradual transitions, illumination changes, object and
camera motion, and dataset-dependent evaluation protocols
\cite{seridi2020survey,kar2024review}. These failure modes are amplified in
short videos, where edits are dense and effects can be visually similar to
true transitions.

\textbf{Deep SBD models.} Deep SBD models learn temporal patterns that are
difficult to encode manually \cite{tran2015c3d,esteve2023shot}, ranging
from hierarchical clustering for broadcast reuse \cite{baraldi2015shot} to
large-scale spatiotemporal CNNs \cite{hassanien2017deepsbd}. TransNet
casts SBD as dense frame-level prediction over low-resolution frame
sequences \cite{soucek2019transnet}. TransNetV2 extends this design with
dilated 3-D convolutions, frame-similarity features, color histograms, and
dual prediction heads for single-frame and all-transition labels
\cite{soucek2020transnetv2}. These models provide fast and accurate
baselines, but their decision quality still depends on thresholded
frame-level scores, making calibration and temporal stability important for
deployment.

\textbf{AutoShot and short-video SBD.} Most established SBD datasets, such
as BBC, RAI, and ClipShots, emphasize documentaries, broadcast footage, or
longer user-generated videos. AutoShot addresses the short-video setting by
introducing SHOT, a dataset with brief clips, dense editing, vertical
layouts, complex gradual transitions, and heavy visual effects
\cite{zhu2023autoshot}. AutoShot uses NAS
\cite{white2023_nas1000,ren2020_nas_survey,elsken2019nas} to search over
approximately 83.9 million candidate architectures composed of 3-D
separable convolution blocks and temporal Transformer blocks
\cite{vaswani2017attention}. The search trains a single-path one-shot
supernet \cite{guo2020spos} and explores architectures with Bayesian
optimization rather than differentiable relaxation \cite{liu2019darts}.
Although the searched backbone improves SHOT performance, repeating the
search and retraining pipeline is computationally costly. AutoShotV2
therefore asks how much can be gained by keeping this representation frozen
and refining only the decision stage.

\textbf{Imbalance, calibration, and temporal smoothing.} Frame-level SBD is
severely imbalanced because boundary frames are rare. Focal Loss reduces
the contribution of easy examples and is a natural alternative to BCE
\cite{lin2017focal}, while soft and neighborhood-expanded targets such as
label smoothing \cite{muller2019label} motivate the boundary-aware many-hot
supervision explored in this paper. SBD is also threshold-sensitive:
temperature scaling rescales logits without changing their ranking
\cite{guo2017calibration}, while richer alternatives such as Platt scaling
\cite{platt1999probabilistic} and isotonic regression
\cite{zadrozny2002transforming} require more calibration data. Measuring
calibration is itself nontrivial under sparse positives, because
equal-width ECE can be dominated by the majority class; this motivates
adaptive and class-conditional estimators \cite{nixon2019measuring}.
AutoShotV2 evaluates these mechanisms separately so that improvements from
training losses and post-processing are not conflated.

\textbf{Efficient adaptation of frozen representations.} Reusing a
pretrained backbone without updating it is a common strategy, from linear
probing of frozen features to parameter-efficient modules such as adapters
\cite{houlsby2019parameter} and low-rank updates \cite{hu2022lora}. Our
setting is deliberately conservative: the searched AutoShot representation
is fully frozen, a small classification head is trained on cached features,
and the final adaptation happens through validation-selected calibration
and smoothing. This keeps adaptation inexpensive and auditable, while also
exposing the limits of a frozen representation under the ClipShots domain
shift.
