\section{Frozen-Feature Study Design}

\subsection{Problem Formulation}

Given a video with $T$ frames, SBD predicts a binary boundary sequence
$\{\hat b_t\}_{t=1}^{T}$. A model first produces frame-level logits $z_t$.
After calibration and smoothing, the final decision is
\begin{equation}
    \hat b_t = \mathbb{1}[\tilde p_t > \theta].
\end{equation}
Consecutive positive predictions are grouped into one transition interval.
Evaluation uses the canonical interval matcher with a tolerance of
$\pm\PaperMatchTolerance$ frames.

\subsection{Frozen AutoShot Representation}

AutoShot \cite{zhu2023autoshot} searches a short-video backbone composed of
3-D convolutional, similarity, histogram, and optional temporal blocks.
Repeating this search is outside the intended adaptation budget. We freeze the
searched backbone and cache its 4864-dimensional feature vector
$h_t\in\mathbb{R}^{4864}$ for each frame. The selected A1 control trains only
a compact decision head:
\begin{equation}
    u_t = \mathrm{Dropout}(\mathrm{ReLU}(W_f h_t+c_f)),\qquad
    z_t = W_c u_t+c_c,
\end{equation}
where $W_f\in\mathbb{R}^{1024\times4864}$. The implementation retains a second
output for controlled auxiliary-label ablations, but its loss weight is zero
for A1 and the deployed B4 pipeline uses only the primary logit $z_t$.

The selected training objective is binary cross-entropy:
\begin{equation}
    \mathcal{L}_{\mathrm{BCE}}
    = -y_t\log\sigma(z_t)-(1-y_t)\log(1-\sigma(z_t)).
\end{equation}
This choice is empirical rather than assumed: the controlled experiments show
no measurable benefit from replacing it with Focal Loss or adding many-hot
auxiliary supervision.

\begin{figure*}[!t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[
    node distance=0.75cm and 1.0cm,
    font=\footnotesize,
    block/.style={draw, rounded corners=2pt, thick, align=center, minimum height=0.9cm, text width=2.65cm},
    arr/.style={-{Stealth[length=5pt]}, thick}
]
\node[block, fill=blue!10] (in) {Video frames\\$48\times27$ RGB};
\node[block, fill=green!12, right=of in] (backbone) {Frozen AutoShot\\feature extractor};
\node[block, fill=green!8, right=of backbone] (feat) {Cached features\\4864-D};
\node[block, fill=orange!15, right=of feat] (head) {BCE primary head\\A1 control};
\node[block, fill=purple!12, right=of head] (temp) {Temperature scaling\\$T=\PaperTemperature$};
\node[block, fill=pink!14, right=of temp] (smooth) {Gaussian smoothing\\$\sigma=\PaperGaussianSigma$};
\node[block, fill=blue!8, right=of smooth] (out) {Fixed threshold\\$\theta=\PaperDeployThreshold$};
\draw[arr] (in) -- (backbone);
\draw[arr] (backbone) -- (feat);
\draw[arr] (feat) -- (head);
\draw[arr] (head) -- (temp);
\draw[arr] (temp) -- (smooth);
\draw[arr] (smooth) -- (out);
\end{tikzpicture}
}
\caption{Selected AutoShotV2 pipeline. B4 applies validation-selected
temperature scaling and Gaussian smoothing to the controlled A1 BCE logits.}
\label{fig:pipeline}
\end{figure*}

\subsection{Validation-Only Protocol Selection}

Temperature scaling rescales the primary logit without changing its ranking:
\begin{equation}
    p_t^{\mathrm{cal}}=\sigma\left(\frac{z_t}{T}\right).
\end{equation}
Temperature scaling changes score calibration but cannot remove isolated
temporal peaks. We therefore apply a one-dimensional Gaussian filter,
\begin{equation}
    \tilde p_t=\sum_k G_{\sigma}(k)p_{t-k}^{\mathrm{cal}},
\end{equation}
We select the complete operating point using five-fold validation. Folds are
stratified by source dataset. For each held-out fold, temperature is fitted on
the other four folds by minimizing binary cross-entropy. We search
$\sigma\in\{0,1,2,3\}$ and
$\theta\in\{0.05,0.10,\ldots,0.50\}$, scoring each pair by mean macro-F1
across validation sources and folds. Ties prefer lower smoothing and then the
threshold nearest 0.10. After selecting $\sigma$ and $\theta$, the final
temperature is fitted on all validation videos. This procedure selects
$T=\PaperTemperature$, $\sigma=\PaperGaussianSigma$, and
$\theta=\PaperDeployThreshold$. The manifest containing folds, key hashes,
search space, and selected values is written before test evaluation. We denote
the resulting A1 plus temperature plus Gaussian configuration B4.

\subsection{Cache and Run Provenance}

The revised pipeline separates a fixed data seed from the training seed.
Before feature extraction, it deterministically selects the training-video
list and hashes that exact list. A sample cache is reusable only when its schema
version, metadata hash, base-checkpoint hash, selected-key hash, video budget,
sampling parameters, boundary width, and data seed all match. Each run writes
the selected video IDs, per-video sample counts, skipped inputs, configuration,
checkpoint hash, and logit-key hash. This strict identity replaces the earlier
path-tolerant cache check that could not prove which 400 videos produced the
historical cache.

\subsection{Training-Time Alternatives}

We evaluate Focal Loss and boundary-aware many-hot targets as alternatives,
not as components of the selected method. For binary targets, the implemented
Focal Loss is
\begin{equation}
    \mathcal{L}_{\mathrm{focal}}
    =-\alpha_t(1-p_t^*)^\gamma\log(p_t^*),
\end{equation}
where $p_t^*=p_t$ for a positive target and $1-p_t$ otherwise, and
$\alpha_t=\alpha y_t+(1-\alpha)(1-y_t)$. The experiments use
$\gamma=1$ and $\alpha=0.5$. The many-hot alternative expands each boundary
label by one neighboring frame and applies an auxiliary loss with weight 0.3.
These variants are retained in the ablation to establish that the B4 gain
comes primarily from post-processing.
