\section{Experiments}

\subsection{Datasets and Training Setup}

We evaluate on the 200-video SHOT test split \cite{zhu2023autoshot}, all 11
BBC Planet Earth videos \cite{baraldi2015shot}, and the 500-video ClipShots
test split \cite{tang2018clipshots}. SHOT is the primary short-video
benchmark; BBC tests long documentary footage with many smooth gradual
transitions; ClipShots tests open-world transfer. Table~\ref{tab:datasets}
summarizes their characteristics.

\begin{table}[!t]
\caption{Dataset Characteristics Used for SBD Evaluation}
\label{tab:datasets}
\centering
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{2.5pt}
\begin{tabular}{L{0.95in}C{0.78in}C{0.85in}C{0.62in}}
\toprule
\textbf{Property} & \textbf{BBC} & \textbf{ClipShots} & \textbf{SHOT} \\
\midrule
Content type & Documentary & Open-world video & Short video \\
Total videos & 11 & 4,039 & 853 \\
Evaluation videos & 11 & 500 & 200 \\
Avg. video length & 2,945 s & 237 s & 39.5 s \\
Avg. shot length & 6.57 s & 15.34 s & 2.59 s \\
Hard cuts & Many & 128,000+ & 8,890 \\
Gradual transitions & Many & 38,000+ & 2,716 \\
Main challenge & Gradual trans. & Diverse effects & Fast editing \\
\bottomrule
\end{tabular}
\end{table}

AutoShotV2 trains only the classification head with Adam at a constant
learning rate; Table~\ref{tab:hyperparams} lists the hyperparameters and how
each was selected. Performance is measured by precision, recall, and F1,
micro-averaged from transition-level TP/FP/FN counts with a matching
tolerance of $\pm\PaperMatchTolerance$ frames.

\begin{table}[!t]
\caption{AutoShotV2 Hyperparameters}
\label{tab:hyperparams}
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{L{1.25in}C{0.7in}L{0.85in}}
\toprule
\textbf{Component} & \textbf{Value} & \textbf{Selection} \\
\midrule
Focal Loss $\gamma$ & 1.0 & Grid search \\
Focal Loss $\alpha$ & 0.5 & Grid search \\
Learning rate & $10^{-5}$ & Adam, constant \\
Weight decay & $10^{-4}$ & Fixed \\
Batch size & 512 & Frame-level \\
Maximum epochs & 20 & Fixed budget \\
Dropout & 0.5 & Fixed \\
Many-hot weight & 0.3 & Validation \\
Gaussian $\sigma$ & \PaperGaussianSigma{} & Validation \\
Deploy temperature $T^{*}$ & \PaperDeployTemperature{} & Validation BCE \\
\bottomrule
\end{tabular}
\vspace{0.5ex}
\noindent{\footnotesize Note: Focal Loss and many-hot parameters are training-loss options evaluated in the ablation study (Section~\ref{sec:ablation}); the controlled B4 replication uses binary cross-entropy (BCE) with one-hot labels.}
\end{table}

\subsection{Evaluation Tracks and Reproducibility Tiers}
\label{sec:tracks}

The paper separates deployment evaluation from controlled component analysis.
\emph{Track 1 (deployed checkpoint)} provides the fixed-threshold deployment results: the head
trained for deployment with the fixed configuration
$T^{*}=\PaperDeployTemperature$, $\sigma=\PaperGaussianSigma$, and
$\theta=\PaperDeployThreshold$. We regenerated its test logits from the local
video splits with full coverage (200/200 SHOT, 11/11 BBC, and 500/500
ClipShots videos) and checksum the resulting logits and result JSON files.
\emph{Track 2 (controlled replication)} retrains the head under the frozen
validation-only protocol of Section~\ref{sec:protocol} (configuration B4) with
full logit caches. Paired bootstrap intervals, calibration diagnostics,
ablations, and the seed study are anchored on this controlled track. Because
the replication was trained in a separate environment with its own validation
pool, its absolute scores differ slightly from the deployed checkpoint. To
avoid mixing absolute scales, replication analyses are reported as
\emph{differences} against the internal BCE control (A1), while absolute F1
values for deployment in the paper refer to the deployed checkpoint.

\subsection{Main Results and Deployment Analysis}
\label{subsec:main_results}

Table~\ref{tab:overall} reports the main comparison under oracle upper-bound configuration and operating-point selection. This protocol selects the best configuration and decision threshold for each evaluation dataset to estimate the best attainable performance of the frozen-feature refinement pipeline. Because this protocol is not a single-threshold deployment setting, we report the fixed deployment results separately below.

Under this oracle protocol, AutoShotV2 reaches peak F1 scores of 0.8607 on SHOT, 0.9656 on BBC, and 0.7706 on ClipShots. These outcomes outperform the reproduced AutoShot baseline (0.8405 on SHOT, 0.9554 on BBC, and 0.7649 on ClipShots) by 2.02, 1.02, and 0.57 percentage points, respectively. On BBC, this configuration outperforms the reproduced TransNetV2 baseline (0.9593) by 0.63 percentage points.

On ClipShots, the peak F1 score of 0.7706 (Table~\ref{tab:extra_sweep_peaks}) also outperforms the reported literature scores of DSM~\cite{tang2018clipshots} (0.7030) by 6.76 percentage points and TransNet (V1)~\cite{soucek2019transnet} (0.7350) by 3.56 percentage points, and exceeds the reproduced TransNetV2 baseline (0.7454) by 2.52 percentage points. To distinguish protocol sources, baseline labels indicate whether they are cited from literature or evaluated within our pipeline. Specifically, reproduced baselines are evaluated using our pipeline, whereas reported baselines (for DSM, TransNet, and TransNetV2 on SHOT) are cited from their original publications. Note that the TransNetV2 model was not evaluated on SHOT in the original work; the reported SHOT score of 0.7993 is cited from \cite{zhu2023autoshot}.

\begin{table}[!t]
\caption{F1 Score Comparison Across Evaluation Datasets}
\label{tab:overall}
\centering
\small
\renewcommand{\arraystretch}{1.08}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{L{2.15in}C{0.55in}C{0.55in}C{0.7in}}
\toprule
\textbf{Method} & \textbf{SHOT} & \textbf{BBC} & \textbf{ClipShots} \\
\midrule
\PaperMainResultRows
\bottomrule
\end{tabular}
}
\vspace{0.5ex}
\noindent{\footnotesize $^\dagger$ Oracle upper-bound result under per-dataset best selection across the evaluated AutoShotV2 configurations. SHOT and ClipShots use the supplemental configuration; BBC uses the primary deployment configuration because it exceeds the supplemental BBC peak. Fixed-threshold deployment results are reported in the preceding row.}
\end{table}

\paragraph{Fixed-threshold deployment}
Under a single fixed deployment threshold ($\theta = \PaperDeployThreshold$), AutoShotV2 achieves 0.8545 on SHOT, 0.9656 on BBC, and 0.7529 on ClipShots. Performance on SHOT and BBC remains strong, but the ClipShots drop from 0.7706 to 0.7529 highlights that domain-specific operating-point selection accounts for the remaining gap.

\subsection{Supplemental Oracle Analysis}
\label{sec:oracle_sweep}

A supplemental configuration ($T^* = 0.2413$, $\sigma = 2.0$, Focal Loss $\gamma = 2.0$, $\alpha = 0.6$, many-hot weight $0.3$, learning rate $7 \times 10^{-6}$) investigates whether stronger focusing and a lower learning rate improve peak F1 under a per-dataset upper-bound threshold sweep.

\begin{table}[!t]
\caption{Peak F1 Scores Under Oracle Upper-Bound Analysis of the Supplemental Configuration}
\label{tab:extra_sweep_peaks}
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{lcccc}
\toprule
\textbf{Dataset} & \textbf{Best Threshold} & \textbf{Precision} & \textbf{Recall} & \textbf{Peak F1} \\
\midrule
SHOT & 0.12 & 0.8408 & 0.8816 & \textbf{0.8607} \\
ClipShots & 0.19 & 0.7011 & 0.8554 & \textbf{0.7706} \\
BBC & 0.12 & 0.9668 & 0.9628 & 0.9648 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:extra_sweep_peaks} shows that the supplemental configuration yields higher peaks on SHOT (+0.62~pp) and ClipShots (+1.77~pp) than the primary configuration. The ``per-dataset best'' row in Table~\ref{tab:overall} selects the best source per dataset: SHOT and ClipShots from the supplemental configuration, BBC from the primary (0.9656 vs.\ 0.9648). However, under a unified threshold ($\theta = 0.17$) the supplemental average F1 (0.8566) falls below the primary deployment average (0.8577), so we retain the primary configuration for fixed-threshold deployment.

\subsection{Recall-Oriented Variant: AutoShotV2-HeatMap}
\label{sec:heatmap_variant}

Because gradual transitions account for most false negatives, we evaluate a
training variant, \emph{AutoShotV2-HeatMap}, that targets recall. The intuition
is that a hard one-hot target poorly matches the spread-out nature of a gradual
transition, whose boundary extends over several frames rather than a single
sharp cut. The variant keeps the frozen AutoShot@F1 backbone and retrains only
the classification head with: (i) \textbf{soft heatmap labels} formed by a
Gaussian ($\sigma_{\text{label}} = 3.0$) placed around each boundary frame, so
neighboring frames receive smoothly decaying targets instead of an abrupt zero;
(ii) \textbf{asymmetric label smoothing} ($\varepsilon = 0.1$) applied only to
positive targets ($1.0 \rightarrow 0.9$), leaving negatives at $0$; and
(iii) Focal Loss ($\gamma = 2.0$, $\alpha = 0.6$), many-hot weight $0.3$, and
mixed-precision (AMP fp16) training. Post-processing uses $T^{*} = 0.268$ and
$\sigma = 2.0$, and the 200 SHOT test videos are excluded from training to
prevent leakage. Evaluation uses the same \texttt{mAP\_f1\_p\_fix\_r} protocol
as above, so the scores are directly comparable to the deployed AutoShotV2.

\begin{table}[!t]
\caption{AutoShotV2-HeatMap Versus AutoShotV2 (Recall-Oriented Operating Point)}
\label{tab:heatmap_variant}
\centering
\small
\renewcommand{\arraystretch}{1.08}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{L{1.35in}C{0.5in}C{0.4in}C{0.55in}C{0.55in}C{0.5in}}
\toprule
\textbf{Model} & \textbf{Dataset} & \textbf{$\theta$} & \textbf{Prec.} & \textbf{Recall} & \textbf{F1} \\
\midrule
AutoShotV2 & SHOT & 0.10 & \PaperDeployShotPrecision & \PaperDeployShotRecall & \PaperDeployShotFOne \\
AutoShotV2-HeatMap & SHOT & 0.10 & 0.8324 & \textbf{0.8804} & 0.8557 \\
\midrule
AutoShotV2 & ClipShots & 0.10 & \PaperDeployClipPrecision & \PaperDeployClipRecall & \PaperDeployClipFOne \\
AutoShotV2-HeatMap & ClipShots & 0.15 & 0.6727 & 0.8629 & 0.7560 \\
\midrule
AutoShotV2 & BBC & 0.10 & -- & -- & \PaperDeployBBCFOne \\
AutoShotV2-HeatMap & BBC & -- & -- & -- & -- \\
\bottomrule
\end{tabular}
}
\vspace{0.5ex}
\noindent{\footnotesize ``--'' marks the BBC entries: the variant was not evaluated on BBC because the source videos were unavailable in our local environment. AutoShotV2-HeatMap rows report the threshold at which the variant peaks per dataset (SHOT peaks at $\theta = 0.10$).}
\end{table}

As summarized in Table~\ref{tab:heatmap_variant}, AutoShotV2-HeatMap is a
\emph{recall-oriented operating point} rather than a higher-F1 model. On SHOT,
at the same deployment threshold $\theta = 0.10$, recall rises from
\PaperDeployShotRecall{} to $0.8804$ ($+2.67$~pp) while F1 stays comparable
(\PaperDeployShotFOne{} $\rightarrow 0.8557$); the recall gain is traded for
lower precision (\PaperDeployShotPrecision{} $\rightarrow 0.8324$). This is
direct evidence that soft heatmap labels recover more boundaries, particularly
gradual transitions. On ClipShots, the variant reaches F1 $= 0.7560$ (at
$\theta = 0.15$), comparable to the AutoShotV2 fixed-threshold deployment
(\PaperDeployClipFOne{}) and still below the oracle peak
(\PaperBestClipFOne{}), with the same low-precision/high-recall pattern.
Importantly, the variant does \emph{not} exceed the AutoShotV2 oracle peak
(\PaperBestShotFOne{} on SHOT) in F1: its value lies in shifting the operating
point toward recall at a fixed threshold, not in raising the capability
ceiling. We therefore position AutoShotV2-HeatMap as a complementary
configuration for applications where missed boundaries are costlier than false
alarms (for example, editorial pre-processing or content indexing), widening the
precision--recall trade-off space rather than replacing the balanced deployment
model.

\subsection{Controlled Component Analysis}

All remaining analyses use Track 2: the controlled B4 replication whose
protocol is summarized in Table~\ref{tab:protocol}.

\begin{table}[!t]
\caption{Fixed Reproducible Evaluation Protocol (Controlled Track)}
\label{tab:protocol}
\centering
\small
\renewcommand{\arraystretch}{1.08}
\begin{tabular}{L{1.45in}L{1.55in}}
\toprule
\textbf{Item} & \textbf{Setting} \\
\midrule
Training objective & BCE, one-hot labels \\
Training / data seed & 42 / 42 \\
Training budget & 20 epochs, batch size 512 \\
Sampling & At most 160 frames/video, 3 negatives/positive \\
Validation size & 200 videos \\
Validation selection & 5 source-stratified folds \\
Selection criterion & Mean macro-F1 across sources/folds \\
Selected temperature & \PaperBFourTemperature \\
Gaussian smoothing & $\sigma=\PaperGaussianSigma$ \\
Decision threshold & $\theta=\PaperDeployThreshold$ \\
Matching tolerance & $\pm\PaperMatchTolerance$ frames \\
Bootstrap & 10,000 video resamples, seed 42 \\
\bottomrule
\end{tabular}
\end{table}

Relative to the A1 control, the selected B4 configuration improves SHOT by
\PaperBFourVsAOneShotPP{} percentage points and ClipShots by
\PaperBFourVsAOneClipPP{} percentage points in F1, while BBC is unchanged after
rounding.
Temperature scaling alone preserves the validation-selected decision threshold;
Gaussian smoothing is the component that changes boundary decisions.

Table~\ref{tab:paired_delta} bootstraps the per-video difference between A1
at its validation-selected threshold and B4 at its frozen configuration
(10,000 paired video resamples). The intervals support positive B4 deltas
on SHOT and ClipShots. The BBC interval contains zero, so we make no
improvement claim for that dataset; BBC also has only 11 sampling units, so
its interval should be interpreted cautiously.

\begin{table}[!t]
\caption{Paired Video Bootstrap Difference, B4 Minus A1 (Absolute Percentage Points)}
\label{tab:paired_delta}
\centering
\small
\renewcommand{\arraystretch}{1.08}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{L{0.8in}C{0.6in}C{1.25in}C{0.65in}}
\toprule
\textbf{Dataset} & \textbf{$\Delta$F1 (pp)} & \textbf{95\% CI (pp)} & \textbf{Excl. 0} \\
\midrule
\PaperPairedDeltaRows
\bottomrule
\end{tabular}
}
\end{table}

\subsection{Calibration Diagnostics}

We evaluate frame probabilities on the combined 200-video validation split
using negative log-likelihood (NLL), Brier score, expected calibration error
with 15 equal-width bins (ECE), equal-mass adaptive ECE (AECE), and
class-balanced ECE (B-ECE). Table~\ref{tab:calibration_metrics} shows that
temperature scaling improves all diagnostics on this split. The much larger
B-ECE reveals that aggregate frame metrics are dominated by negative frames.
Because the same validation split fits temperature, these values are used as
diagnostics rather than as untouched calibration estimates.

\begin{table}[!t]
\caption{Frame-Level Validation Calibration Diagnostics}
\label{tab:calibration_metrics}
\centering
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{2pt}
\begin{tabular}{L{0.85in}C{0.45in}C{0.45in}C{0.45in}C{0.45in}C{0.45in}}
\toprule
\textbf{Variant} & \textbf{NLL} & \textbf{Brier} & \textbf{ECE} & \textbf{AECE} & \textbf{B-ECE} \\
\midrule
\PaperCalibrationMetricRows
\bottomrule
\end{tabular}
\end{table}

A reliability diagram is provided in the supplementary artifacts.

Table~\ref{tab:test_calibration} reports test-set calibration using the
temperature selected on validation. ClipShots has the largest B-ECE despite
a small aggregate ECE, consistent with domain-shifted false positives.

\begin{table}[!t]
\caption{Test Calibration at the Validation-Selected Temperature}
\label{tab:test_calibration}
\centering
\scriptsize
\renewcommand{\arraystretch}{1.08}
\setlength{\tabcolsep}{2pt}
\begin{tabular}{L{0.45in}C{0.47in}C{0.47in}C{0.47in}C{0.47in}C{0.47in}}
\toprule
\textbf{Dataset} & \textbf{NLL} & \textbf{Brier} & \textbf{ECE} & \textbf{AECE} & \textbf{B-ECE} \\
\midrule
\PaperTestCalibrationRows
\bottomrule
\end{tabular}
\end{table}

\subsection{Controlled Training Ablation}
\label{sec:ablation}

Table~\ref{tab:ablation} reports the outcome of the design space of
Section~\ref{sec:objectives} as F1 differences against the A1 control. A2,
A3, and B1 show that Focal Loss and many-hot supervision do not improve the
control. B5 combines these training changes with B4 post-processing and is
numerically similar on SHOT but slightly weaker on BBC and ClipShots. The
observed gain therefore comes from calibrated post-processing rather than
from the more complex training objective. A0 is omitted because its per-dataset
best-threshold protocol is not a direct controlled comparison.

\begin{table}[!t]
\caption{Controlled Phase 2 Ablation: $\Delta$F1 Against the A1 BCE Control (Percentage Points)}
\label{tab:ablation}
\centering
\scriptsize
\renewcommand{\arraystretch}{1.04}
\setlength{\tabcolsep}{2pt}
\begin{tabular}{L{1.7in}C{0.4in}C{0.4in}C{0.4in}}
\toprule
\textbf{Configuration} & \textbf{SHOT} & \textbf{BBC} & \textbf{ClipShots} \\
\midrule
\PaperAblationDeltaRows
\bottomrule
\end{tabular}
\end{table}

\subsection{Efficiency and Reproducibility}

The backbone remains frozen, so only the Phase 2 head is optimized.
Table~\ref{tab:efficiency} reports parameter and run-artifact statistics.
The CPU post-processing measurement covers temperature scaling and Gaussian
smoothing on cached logits. End-to-end video decoding and backbone inference
are excluded. The original run artifact did not retain elapsed training time,
so we do not estimate or reconstruct it.

\begin{table}[!t]
\caption{Efficiency and Run-Artifact Statistics}
\label{tab:efficiency}
\centering
\small
\renewcommand{\arraystretch}{1.06}
\begin{tabular}{L{1.9in}L{1.05in}}
\toprule
\textbf{Item} & \textbf{Value} \\
\midrule
\PaperEfficiencyRows
\bottomrule
\end{tabular}
\end{table}



\subsection{Training-Seed Robustness}
\label{sec:seed_robustness}

To quantify optimization variability, we retrained the BCE one-hot head
\PaperSeedCount{} times with training seeds 42, 43, and 44 while holding the
data seed, the training-video selection, and the sample cache identity fixed.
Each run selected its own post-processing configuration with the frozen
five-fold validation-only protocol of Section~\ref{sec:protocol} before any
test evaluation. Consistent with the delta-only reporting of
Section~\ref{sec:tracks}, we summarize this study by its dispersion: the
sample standard deviation of test F1 across seeds is
\PaperSeedShotFOneStd{} percentage points on SHOT,
\PaperSeedBBCFOneStd{} percentage points on BBC, and
\PaperSeedClipFOneStd{} percentage points on ClipShots --- below
0.5 percentage points on every dataset and an
order of magnitude smaller than the paired bootstrap interval widths of
Table~\ref{tab:paired_delta}. In these runs, head-training randomness is a
smaller source of variation than video sampling. This study isolates
training-seed sensitivity end to end, complementing the component analysis of
Table~\ref{tab:ablation}.

\subsection{Limitations}

The study has four important limitations. First, the historical sample cache recorded 400
videos and 33,174 frames but not the selected IDs; the current manifests fix
this for future runs but cannot reconstruct the old cache contents. Second,
validation calibration diagnostics reuse the temperature-selection data. Third,
the frozen representation does not fully control cross-domain false
positives on ClipShots. An exploratory experiment that partially unfroze the
layer nearest to the classification head reached a ClipShots F1 of 0.7962
but degraded BBC to 0.9341, confirming a multi-domain trade-off that the
fully-frozen regime avoids at the cost of lower ClipShots precision. This
trade-off is not analyzed further in the present paper, which focuses
exclusively on the frozen-feature setting.
Fourth, the main comparison is an oracle upper-bound analysis with domain-specific threshold tuning rather than a single unified deployment setting. In practice, finding domain-specific thresholds requires labeled data from the target distribution, meaning that the peak F1 scores of 0.8607 on SHOT and 0.7706 on ClipShots should be interpreted as potential estimates of frozen-feature capability rather than out-of-the-box deployment results.
