\section{Conclusion}

We presented AutoShotV2, a compact refinement framework for short-video shot
boundary detection. The method freezes the NAS-searched AutoShot backbone,
trains a lightweight classification head on cached features, and applies
temperature scaling and Gaussian smoothing before thresholding. With a
single fixed deployment configuration, AutoShotV2 reaches F1 scores of
\PaperDeployShotFOne{} on SHOT, \PaperDeployBBCFOne{} on BBC, and
\PaperDeployClipFOne{} on ClipShots without repeating the architecture
search.

The controlled replication clarifies the source of the improvement. Focal
Loss and many-hot supervision do not produce consistent practical gains over
the BCE control, whereas calibrated post-processing yields paired-bootstrap gains on SHOT and
ClipShots. The three-seed study observes F1 standard deviation below
0.5 percentage points on every dataset, and the class-balanced calibration
error shows why very
small aggregate ECE values should not be interpreted as indicating uniformly calibrated
boundary probabilities. Most reported tables are regenerated from tracked
result artifacts; controlled analyses include cache identities and
frozen selection manifests.

Cross-domain analysis highlights a key remaining challenge: on open-world
ClipShots the dominant loss is precision, as visual effects and domain shift
create false-positive peaks that survive smoothing. Potential avenues for future work include reserving an independent calibration split,
extending calibration to boundary-conditional estimates, and exploring
domain-adaptive components such as lightweight adapters on the frozen backbone
or per-domain post-processing selection, together with multimodal cues such as
audio when visual evidence alone is ambiguous.
