\begin{abstract}
Shot boundary detection (SBD) is a fundamental preprocessing step for video
indexing, retrieval, summarization, and automated editing. Modern short-video
platforms create a difficult operating regime: videos are brief, shots are
extremely short, transitions are visually complex, and boundary frames are
rare compared with non-boundary frames. This paper presents AutoShotV2, a
lightweight improvement over the AutoShot architecture for short-video SBD.
Instead of re-searching or retraining the full backbone, AutoShotV2 freezes
the AutoShot feature extractor and trains a new two-branch classification
head over 4864-dimensional cached features, exploring complementary one-hot
and boundary-aware many-hot supervision. At inference time, the primary
boundary logits are calibrated by temperature scaling and stabilized by
one-dimensional Gaussian smoothing before thresholding. With a fixed
deployment configuration ($T^{*}=\PaperDeployTemperature$), AutoShotV2
reaches an F1-score of \PaperDeployShotFOne{} on the SHOT test set of 200
short videos, improving over the reproduced AutoShot baseline by
\PaperDeployVsAutoShotPP\% and over the reported TransNetV2
baseline by \PaperDeployVsTransNetPP\% in absolute F1, and transfers to BBC
documentary footage (\PaperDeployBBCFOne) while remaining limited on
open-world ClipShots (\PaperDeployClipFOne). A controlled replication under
a frozen validation-only protocol shows that the gain comes from calibrated
post-processing rather than the training-loss alternatives, with paired
bootstrap intervals supporting improvements on SHOT and ClipShots but not
BBC. Temperature scaling reduces validation NLL from 0.013006 to 0.009591
and equal-width ECE from 0.007149 to 0.002214, while class-balanced ECE
remains 0.070405, showing that aggregate frame-level calibration metrics are
optimistic under severe boundary sparsity. A three-seed replication bounds
training-seed F1 variability below 0.5\% on every dataset. We release
validation-selection manifests, per-video statistics, analysis code, and
checksum-oriented artifact tooling.
\end{abstract}
